Individual heterogeneity in the functional network topography of medial prefrontal

### 2019-09-06 Manuscript.Rmd
apa citation tweaks

### *Correlation vs community detection in mPFC*

``` {r Correlation vs community detection: compute, fig.align = "center", echo = FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
# Spearman to avoid issues with the differences in value ranges
unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- unthreshComm_PFC_halves_plot
D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1, D2)
subjList_halves_plot <- rep(best$SubjID, each = 2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))

@@

# stats: one sample t's per hemisphere/region
curvCors %>% group_by(region, Hemisphere) %>% 
  summarise(TStat = t.test(Correlation)$statistic,
            p = t.test(Correlation)$p.val,
            Sig = p < 0.05,
            ES = DescTools::CohenD(Correlation))

>>>>

### *Correlation vs community detection in mPFC*

``` {r Correlation vs community detection: compute, fig.align = "center", echo = FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
# Spearman to avoid issues with the differences in value ranges
unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- unthreshComm_PFC_halves_plot
D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1, D2)
subjList_halves_plot <- rep(best$SubjID, each = 2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))

@@

# stats: one sample t's per hemisphere/region
curvCors %>% group_by(region, Hemisphere) %>% 
  summarise(medianCor = median(Correlation),
            seCor = sd(Correlation) / sqrt(nSubj),
            TStat = t.test(Correlation)$statistic,
            p = t.test(Correlation)$p.val,
            Sig = p < 0.05,
            ES = DescTools::CohenD(Correlation))
